%Critically evaluate your project: what worked well, and what didn't? how
%did you do relative to your plan? what changes were the result of improved thinking
%and what changes were forced upon you? how did your team work together? etc. Note
%that you need to show that you understand the weaknesses in your work as well as its
%strengths. You may wish to identify relevant future work that could be done on your
%project.
	\subsection{Initial aims}
    	Our primary goal from the outset was to create a system that would allow a user to take a system, make changes to it, and obtain a quantitative output on which they can run statistical analysis and determine the appropriateness of implementing the changes in real life. On this front, the TRATT system has been successful up to the level of accuracy of our model.
        
        Our secondary aim was to produce a GUI to allow for empirical evidence of the system operating appropriately, this works well, but is limited to the preset systems we have in place (one modelling a straight road, and the other a four way intersection. The services available directly to the end user through the UI are:
        \begin{itemize}
        	\item Control over driver behaviour.
            \item Control of traffic light interval.
            \item Control over maximum driver speed.
            \item Control over the decision matrix
        \end{itemize}

	There were several features that we had planned on including, however he found ourselves unable to due to constraints on time and resources, these are listed in the future work section.
    
	\subsection{Possible improvements}
    	We determined that the key improvement we would make if we were assigned this project again would be to model it as a continuous rather than a discrete system for more realistic output.
        
	\subsection{Future work}
		As a group we discussed ways we would improve this project if we were not constrained by time, we came to the conclusion that the following features would be good to implement:
        \begin{description}
        \item{UI} We could enhance the user interface by giving more control to the users, allowing them to input their own maps (and providing them with more preset maps), and change more variables. Perhaps including a few preset decision matrices would be useful too.
        \item{Back end} We could strive for a more realistic traffic model accounting for lane changing, overtaking, and accidents. We could also implement algorithms to show drivers taking optimal paths in more complex scenarios.
       	\item{Vehicles} It would also be good to include more vehicle types, and allow them to follow different behaviour patterns (i.e. emergency vehicles not following standard traffic rules).
        \end{description}
        